Multimodal spatial availability: a singly-constrained measure of accessibility considering multiple modes

### 2024-02-07 Presentations/CIT-Presentation.Rmd
Re-organized repo, checked to make sure all .rmds run. Updated lockfile to reflect current state of package dependencies.

---
title: "Quantifying multi-modal competition using spatial availability"
subtitle: "NECTAR - Sustainable Neighbourhoods"
author: "Anastasia Soukhov, J. Tarriño Ortiz, J. A. Soria-Lara, A. Páez"
date: "21-06-2023"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current% / 17" 
      highlightStyle: github
      highlightLines: true
      ratio: '16:9'
      countIncrementalSlides: false
      beforeInit: "macros.js"
---
```{r xaringan-themer, include=FALSE, warning=FALSE}
#this themer package allows us to change the .css themes through this chunk. Easier than changing the .css directly.
library(xaringanthemer)
style_mono_accent(
  base_color = "#7A003C", #maroon
  link_color = "#5E6A71", #grey
  text_bold_color = "#FDBF57", #gold
  text_slide_number_color = "#FDBF57", #gold
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r load-packages, include=FALSE, cache=FALSE}
library(dplyr)
library(sf)
library(ggplot2)
library(tidyverse)
library(units)
library(patchwork)
library(ggspatial)
library(ggforce)
library(geomtextpath)
library(knitr)
library(kableExtra)
library("ggpmisc")
options(scipen = 999)
```

@@

#write the dataframe long.
od_tt_m <- data.frame(i = c("A", "A", "A", "A", "A", "A",
                            "B", "B", "B", "B", "B", "B",
                            "C", "C", "C", "C", "C", "C"), # Three origins
                    j = c("1", "2", "3", "1", "2", "3", 
                          "1", "2", "3", "1", "2", "3", 
                          "1", "2", "3", "1", "2", "3"), # Three destinations
                    m = c("pt", "pt", "pt", "car", "car", "car",
                          "pt", "pt", "pt", "car", "car", "car",
                          "pt", "pt", "pt", "car", "car", "car"),
                    tt = c(15, 30, 100, 10, 25, 80, #travel time, z-mode (original) AND THEN x-mode (the faster mode)
                           30, 15, 100, 25,  10,  80,
                           100, 100, 15, 80, 80, 10), 
                    pop = c(16666.66666, 16666.66666, 16666.66666, 33333.33333, 33333.33333, 33333.33333,
                            60000, 60000,60000, 90000, 90000, 90000,
                            3000, 3000, 3000, 7000,7000, 7000),
                    opp = c(100000, 100000, 10000, 100000, 100000, 10000,
                            100000, 100000, 10000, 100000, 100000, 10000,
                            100000, 100000, 10000, 100000, 100000, 10000)) 
```

@@

od_table <- data.frame(Center = c("A", "B", "C", "1", "2", "3"),
  Size = c("50,000 pop.", "150,000 pop.", "10,000 pop.", 
           "100,000 jobs", "100,000 jobs", "10,000 jobs"))

@@

```{r, create-figure-with-toy-example, echo=FALSE, eval=FALSE}
toy_example_plot <- ggplot() + 
  # Plot centers
  geom_circle(data = centers,
             aes(x0 = x, 
                 y0 = y,
                 r = radius),
             color = "grey40") +
  annotate(geom = "label", 
           x=c(1.6, 1.7, 7.5),
           y=c(9.1, 0.9, 5.2), 
           size=4, 
           label.size=NA) +
  # Connect origins and destinations with curves
  geom_curve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group),
             curvature = 0.20,
             linewidth = 1,
             color = "black") +
  # Plot origins and destinations
  geom_point(data = od,
            aes(size = size,
                x = x, 
                y = y, 
                color = type,
                shape = type)) +
  scale_size(range = c(6, 16)) +
  # Label origins and destinations
  geom_text(data = od, 
            aes(x, 
                y, 
                label=id), 
            size=4) +
  # Create table
  annotate(geom = 'table',
           x = 9,
           y = 9,
           label = list(od_table),
           size=4) +
  # Theme the plot
  coord_fixed() + 
  theme_void() + guides(shape = "none", size = "none", color = "none", linetype ="none")

toy_example_plot
ggsave("Presentations/toy-example1.png",dpi=600)
```

## Accessibility competition between modes

**Motivation**: interpreting accessibility measures (location-based _potential interaction_) for policy interventions

```{r, toy-example0, out.width='40%', fig.align='center', echo=FALSE}
knitr::include_graphics("Presentations/access-demo.png")
```

---
## Accessibility competition between modes

**Motivation**: interpreting accessibility measures (location-based _potential interaction_) for policy interventions

```{r, toy-example00, out.width='40%', fig.align='center', echo=FALSE}
knitr::include_graphics("Presentations/access-demo.png")
```

### Overview

**1.** Types of current accessibility measures and their limitations

**2.** Multi-modal **spatial availability**

**3.** Planning accessibility policy interventions considering multi-modal competition

---
class: center, middle
## Classification of multi-modal accessibility measures

@@

@@

@@

```{r, toy-example1, out.width='120%', echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```

@@

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```
]

@@

##### Shen-type accessibility
$a_i^m = \sum_j \frac{O_j f^m(c_{ij}^m)}{\sum_m \sum_i P_{i}^m f^m(c_{ij}^m)}$

@@

???
-  ## NOTE: this is competitive for S. you have high access with less demand, A and B are different. It is still unconstrained when you try to retrieve the number of opportunities -- it is the totla population and not the job-seeking population 
---
### Simulated example: competitive and unconstrained

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```

@@

```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```
]

@@

##### Spatial availability per origin and mode
$V^m_{i} = \sum_{j} O_j\ F^{t,m}_{ij}$

@@

### Simulated example: competitive _and_ constrained

.pull-left[
```{r,out.width='120%', echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```
]

@@

##### Spatial availability per origin, per mode
$V_{i} = \sum_{m} V^m_{i}$

@@

```{r, echo=FALSE, message=FALSE}
knitr::kable(V,
             format = "html",
             digits = 2)
```

@@

.pull-left[
```{r, echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics("Presentations/madrid-region.png")
```
]

.pull-right[
```{r, echo=FALSE, out.width='50%', fig.align='center'}
knitr::include_graphics("Presentations/city-centre.png")
```
- November 2018 - LEZ Centro
- 2023 - LEZ within M-30
- 2024 - LEZ within Madrid Municipality 
]

???
A NEEED for multi-modal analysis methods that are interpretive and comparative -- proportional allocation achieves that!
---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentations/im_populations_zn208_plot.png")
```
Worker population, by mode, at resolution Zona 208

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentations/Hansen_im_V_zn208_plot.png")
```
Uncompetitive and unconstrained accessibility $S_i^m$ at resolution Zona 208

@@

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentations/SA_im_V_zn208_plot.png")
```
Spatial Availability $V_i^m$ at resolution Zona 208

@@

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%', fig.align='center'}
knitr::include_graphics("Presentations/SA_i_V_zn208_plot.png")
```
Spatial Availability $V_i$ at resolution Zona 208

@@

- **Scenario evaluation**: accessibility when...
  - LEZ boundaries change
  - Vehicle characteristic restrictions change
  - Travel behaviour changes
  - Spatial unit of analysis changes

- **Questions of equity**: which neighbourhoods, what people, what modes?
  - GHG emission reductions
  - Advantages to non-car users
  - Who are impacted disproportionally

@@

```{r, echo=FALSE, out.width="20%"}
knitr::include_graphics("Presentations/MJ_logo.png")
```

```{r, echo=FALSE, out.width="30%"}
knitr::include_graphics("Presentations/mcm-sci-sees_left-col.png")
```

@@

#### Spatial availability paper:
```{r, echo=FALSE, out.width="10%"}
knitr::include_graphics("Presentations/spatial-availability.png")
```

>>>>

---
title: "Multi-modal spatial availability: a research proposal"
subtitle: "CIT - Tenerife 2023"
author: "Anastasia Soukhov, J. Tarriño Ortiz, J. A. Soria-Lara, A. Páez"
date: "15-06-2023"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current% / 12" 
      highlightStyle: github
      highlightLines: true
      ratio: '16:9'
      countIncrementalSlides: false
      beforeInit: "macros.js"
---
```{r xaringan-themer, include=FALSE, warning=FALSE}
#this themer package allows us to change the .css themes through this chunk. Easier than changing the .css directly.
library(xaringanthemer)
style_mono_accent(
  base_color = "#7A003C", #maroon
  link_color = "#5E6A71", #grey
  text_bold_color = "#FDBF57", #gold
  text_slide_number_color = "#FDBF57", #gold
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r load-packages, include=FALSE, cache=FALSE}
library(dplyr)
library(sf)
library(ggplot2)
library(tidyverse)
library(units)
library(patchwork)
library(ggspatial)
library(ggforce)
library(geomtextpath)
library(knitr)
library(kableExtra)
options(scipen = 999)
```

@@

#write the dataframe long.
od_tt_m <- data.frame(i = c("A", "A", "A", "A", "A", "A",
                            "B", "B", "B", "B", "B", "B",
                            "C", "C", "C", "C", "C", "C"), # Three origins
                    j = c("1", "2", "3", "1", "2", "3", 
                          "1", "2", "3", "1", "2", "3", 
                          "1", "2", "3", "1", "2", "3"), # Three destinations
                    m = c("pt", "pt", "pt", "car", "car", "car",
                          "pt", "pt", "pt", "car", "car", "car",
                          "pt", "pt", "pt", "car", "car", "car"),
                    tt = c(15, 30, 100, 10, 25, 80, #travel time, z-mode (original) AND THEN x-mode (the faster mode)
                           30, 15, 100, 25,  10,  80,
                           100, 100, 15, 80, 80, 10), 
                    pop = c(20000, 20000, 20000, 30000, 30000, 30000,
                            50000, 50000,50000, 100000, 100000, 100000,
                            3000, 3000, 3000, 7000,7000, 7000),
                    opp = c(100000, 100000, 10000, 100000, 100000, 10000,
                            100000, 100000, 10000, 100000, 100000, 10000,
                            100000, 100000, 10000, 100000, 100000, 10000)) 
```

@@

od_table <- data.frame(Center = c("A", "B", "C", "1", "2", "3"),
  Size = c("50,000 pop (40% pt)", "150,000 pop (33% pt)", "10,000 pop (30% pt)", 
           "100,000 jobs", "100,000 jobs", "10,000 jobs"))

@@

```{r, create-figure-with-toy-example, echo=FALSE, eval=FALSE}
toy_example_plot <- ggplot() + 
  # Plot centers
  geom_circle(data = centers,
             aes(x0 = x, 
                 y0 = y,
                 r = radius),
             color = "grey40") +
  annotate(geom = "label", 
           x=c(0.5, 0.6, 7),
           y=c(9, 1, 5.2), 
           label = c("Suburban", "Urban", "Satellite"), 
           size=4, 
           label.size=NA) +
  # Connect origins and destinations with curves
  geom_curve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group),
             curvature = 0.20,
             linewidth = 1,
             color = "black") +
  # Text on curves
  geom_textcurve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group,
                   label = time),
               size = 3.5,
             curvature = 0.20,
             color = "black") +
  # Plot origins and destinations
  geom_point(data = od,
            aes(size = size,
                x = x, 
                y = y, 
                color = type,
                shape = type)) +
  scale_size(range = c(4, 10)) +
  # Label origins and destinations
  geom_text(data = od, 
            aes(x, 
                y, 
                label=id), 
            size=4) +
  # Create table
  annotate(geom = "table",
           x = 9, 
           y = 9, 
           label = list(od_table),
           fill = "white",
           size=3) +
  # Theme the plot
  coord_fixed() + 
  theme_void() + guides(shape = "none", size = "none", color = "none", linetype ="none")

toy_example_plot
ggsave("Presentation-images/toy-example.png",dpi=600)
```
class: center, middle
## Overview of multi-modal accessibility measures

@@

???
<!-- for the title slide --> 
In this presentation I will speak on how current accessibility measures _miss_ considering competition
**1.** Limitations of current accessibility measures
**2.** Explaining **spatial availability** with a multi-modal extension
**3.** Policy scenario planning applications - equity

@@

---
class: center
### Simulated example: uncompetitive and unconstrained

```{r, toy-example0, out.width='80%', echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example.png")
```

---
count: false

@@

```{r, toy-example1, out.width='120%', echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example.png")
```

@@

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example.png")
```
]

@@

##### Shen-type accessibility
$a_i^m = \sum_j \frac{O_j f^m(c_{ij}^m)}{\sum_m \sum_i P_{i}^m f^m(c_{ij}^m)^m}$

@@

???
-  ## NOTE: this is competitive for S. you have high access with less demand, A and B are different. It is still unconstrained when you try to retrieve the number of opportunities -- it is the totla population and not the job-seeking population 
---
count: false
### Simulated example: competitive and unconstrained

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example.png")
```

@@

```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example.png")
```
]

@@

##### Spatial availability
$V^m_{i} = \sum_{j} O_j\ F^{t,m}_{ij}$

@@

---
count: false
### Simulated example: competitive _and_ constrained

.pull-left[
```{r,out.width='120%', echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example.png")
```
]

@@

##### Spatial availability
$V_{i} = \sum_{m} V^m_{i}$

@@

```{r, echo=FALSE, message=FALSE}
knitr::kable(V %>% dplyr::select(-v),
             format = "html",
             digits = 2)
```

@@

.pull-left[
```{r, echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics("Presentation-images/madrid-region.png")
```
]

.pull-right[
```{r, echo=FALSE, out.width='50%', fig.align='center'}
knitr::include_graphics("Presentation-images/city-centre.png")
```
- November 2018 - LEZ Centro
- 2023 - LEZ within M-30
- 2024 - LEZ within Madrid Municipality 
]

???
A NEEED for multi-modal analysis methods that are interpretive and comparative -- proportional allocation achieves that!
---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentation-images/Hansen_im_V_zn208_plot.png")
```
Uncompetitive and unconstrained accessibility $S_i^m$ at resolution Zona 208

@@

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentation-images/SA_im_V_zn208_plot.png")
```
Spatial Availability $V_i^m$ at resolution Zona 208

@@

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%', fig.align='center'}
knitr::include_graphics("Presentation-images/SA_i_V_zn208_plot.png")
```
Spatial Availability $V_i$ at resolution Zona 208

@@

- Scenario evaluation: accessibility when...
  - LEZ boundaries change
  - Vehicle characteristic restrictions change
  - Travel behaviour changes

- Questions of equity: which neighbourhoods, what people, what modes?
  - GHG emission reductions
  - Advantages to non-car users
  - Who is impacted disproportionally

@@

```{r, echo=FALSE, out.width="20%"}
knitr::include_graphics("Presentation-images/MJ_logo.png")
```

```{r, echo=FALSE, out.width="30%"}
knitr::include_graphics("Presentation-images/mcm-sci-sees_left-col.png")
```

@@

#### Spatial availability paper:
```{r, echo=FALSE, out.width="10%"}
knitr::include_graphics("Presentation-images/spatial-availability.png")
```

### 2024-02-07 Presentations/NECTAR-Coimbra-Presentation.Rmd
Re-organized repo, checked to make sure all .rmds run. Updated lockfile to reflect current state of package dependencies.

toy_example_plot
ggsave("Presentations/toy-example1.png",dpi=600)
```

@@

```{r, toy-example0, out.width='40%', fig.align='center', echo=FALSE}
knitr::include_graphics("Presentations/access-demo.png")
```

@@

```{r, toy-example00, out.width='40%', fig.align='center', echo=FALSE}
knitr::include_graphics("Presentations/access-demo.png")
```

@@

```{r, toy-example1, out.width='120%', echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```

@@

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```
]

@@

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```

@@

```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```
]

@@

.pull-left[
```{r,out.width='120%', echo=FALSE}
knitr::include_graphics("Presentations/toy-example1.png")
```
]

@@

.pull-left[
```{r, echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics("Presentations/madrid-region.png")
```
]

.pull-right[
```{r, echo=FALSE, out.width='50%', fig.align='center'}
knitr::include_graphics("Presentations/city-centre.png")
```
- November 2018 - LEZ Centro
- 2023 - LEZ within M-30
- 2024 - LEZ within Madrid Municipality 
]

???
A NEEED for multi-modal analysis methods that are interpretive and comparative -- proportional allocation achieves that!
---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentations/im_populations_zn208_plot.png")
```
Worker population, by mode, at resolution Zona 208

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentations/Hansen_im_V_zn208_plot.png")
```
Uncompetitive and unconstrained accessibility $S_i^m$ at resolution Zona 208

>>>>

toy_example_plot
ggsave("Presentation-images/toy-example1.png",dpi=600)
```

@@

```{r, toy-example0, out.width='40%', fig.align='center', echo=FALSE}
knitr::include_graphics("Presentation-images/access-demo.png")
```

@@

```{r, toy-example00, out.width='40%', fig.align='center', echo=FALSE}
knitr::include_graphics("Presentation-images/access-demo.png")
```

@@

```{r, toy-example1, out.width='120%', echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example1.png")
```

@@

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example1.png")
```
]

@@

.pull-left[
```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example1.png")
```

@@

```{r, out.width='120%',echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example1.png")
```
]

@@

.pull-left[
```{r,out.width='120%', echo=FALSE}
knitr::include_graphics("Presentation-images/toy-example1.png")
```
]

@@

.pull-left[
```{r, echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics("Presentation-images/madrid-region.png")
```
]

.pull-right[
```{r, echo=FALSE, out.width='50%', fig.align='center'}
knitr::include_graphics("Presentation-images/city-centre.png")
```
- November 2018 - LEZ Centro
- 2023 - LEZ within M-30
- 2024 - LEZ within Madrid Municipality 
]

???
A NEEED for multi-modal analysis methods that are interpretive and comparative -- proportional allocation achieves that!
---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentation-images/im_populations_zn208_plot.png")
```
Worker population, by mode, at resolution Zona 208

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentation-images/Hansen_im_V_zn208_plot.png")
```
Uncompetitive and unconstrained accessibility $S_i^m$ at resolution Zona 208

### 2024-02-07 TRB/TRB-Poster.Rmd
Re-organized repo, checked to make sure all .rmds run. Updated lockfile to reflect current state of package dependencies.

---
title: "Multimodal spatial availability: a singly-constrained measure of accessibility considering multiple modes"
poster_height: "36in"
poster_width: "54in"
font_family: 'Rasa'
primary_colour: "#7A003C"
secondary_colour: "#d3d3d3"
accent_colour: "#FDBF57"
titlebox_bordercol: "#5E6A71"
titlebox_borderwidth: "0.2cm"
author:
  - name: Anastasia Soukhov
    affil: 1
    email: soukhoa@mcmaster.ca
    twitter: soukhov_a
    main: true
  - name: Javier Tarriño-Ortiz
    affil: 2
    email: javier.tarrino.ortiz@upm.es
  - name: Julio A. Soria-Lara
    affil: 2
    email: julio.soria-lara@upm.es
  - name: Antonio Páez
    email: paezha@mcmaster.ca
    affil: 1
affiliation:
  - num: 1
    address: Department of Earth, Environment and Society, McMaster University, Hamilton, Canada
  - num: 2
    address: Centro de Investigación del Transporte (TRANSyT), Universidad Politécnica de Madrid, Madrid, Spain
column_numbers: 4
logoright_name: Presentation-images/acknowledgements-combo.png
logoleft_name: Presentation-images/soukhova-LinkTree.png
sectitle_textsize: "40pt"
sectitle_borderwidth: "0.4mm"
title_textsize: "80pt"
author_textsize: "50pt"
affiliation_textsize: "40pt"
body_textsize: "35px"
link-citations: true
bibliography: bibliography/bibliography.bib
output: 
  posterdown::posterdown_html:
    self_contained: true
knit: pagedown::chrome_print  #this knits the created html file into a .pdf. comment out if .pdf isn't needed
---
# Overview
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, eval=FALSE, include=FALSE}
# pagedown::chrome_print("TRB-Poster.Rmd", format = "pdf")
```
```{r load-packages, cache=FALSE, include=FALSE}
library(dplyr)
library(sf)
library(ggplot2)
library(tidyverse)
library(units)
library(patchwork)
library(ggspatial)
library(ggforce)
library(geomtextpath)
library(knitr)
library(gridExtra)
library(grid)
library(huxtable)

@@

quick_html(ht, file = "Presentation-images/synth_ex_table.html", open = FALSE)
# higher zoom increases resolution and image size
webshot::webshot(url = "Presentation-images/synth_ex_table.html", file = "Presentation-images/synth_ex_table.png",
                 zoom = 5, selector = "table")
```
```{r, create-figure-with-toy-example, echo=FALSE, eval=FALSE, include=FALSE}
toy_example_plot <- ggplot() + 
  # Plot centers
  geom_circle(data = centers,
             aes(x0 = x, 
                 y0 = y,
                 r = radius),
             color = "grey30",
             fill = "grey90") +
  annotate(geom = "label", 
           x=c(1.5, 1.5, 10),
           y=c(9.2, 0.8, 5.2), 
           label = c("Suburban (50,000 jobs)", "Urban (100,000 jobs)", "Satellite (10,000 jobs)"),
           fill = c("turquoise1","turquoise1","turquoise1"),
           size=2.7) +
  # Connect origins and destinations with curves and put the text on curves
  geom_textcurve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group,
                   label = time),
             color = "black",
             position=position_jitter(width=0.1,height=0.1),
             size = 1.8,
             curvature = 0.20,
             linewidth = 0.5,
             linecolour = "black",
             arrow = arrow(type = "closed", angle = 10, length = unit(0.03, "npc"))) +
  # Plot origins and destinations points
  geom_point(data = od,
            aes(size = size,
                x = x, 
                y = y, 
                color = id,
                shape = type)) +
  scale_size(range = c(3, 7)) +
  scale_shape_manual(values = c("Population" = 17,'Jobs' = 16)) +
  scale_color_manual(values = c("A" = "springgreen3",
                                "B" = "springgreen4",
                                "C" = "springgreen1",
                                '1' = "turquoise1",
                                '2' = "turquoise1",
                                '3' = "turquoise1")) +
  # Label origins and destinations
  geom_text(data = od, 
            aes(x, 
                y, 
                label=id),
            size=2.5) +
  # place the table
    annotation_custom(rasterGrob(png::readPNG(source="Presentation-images/synth_ex_table.png")),
                      xmin= 5.5, xmax=Inf, 
                      ymin=6, ymax=Inf
                      )+
  # Theme the plot
  coord_fixed(xlim = c(0,20), ylim=c(0,12)) + 
  theme_void() + guides(shape = "none", size = "none", color = "none", linetype ="none")

toy_example_plot
ggsave("Presentation-images/toy-example.png",dpi=600)
```

@@

![_Figure 1: Calculated Hansen $S$, Shen-type $a$ and Spatial Availability $V$ assuming an impedance function of $f(c_{ij})^{\text{x}} = f(c_{ij})^{\text{z}} =exp(-0.1 \cdot c_{ij}^m)$ for the multimodal synthetic population._](Presentation-images/toy-example.png){#id .class width=100%}

@@

![_Figure 2: Spatial distribution of jobs taken by people living and working in Madrid as reported in the 2018 travel survey (left) and trip length distribution (right). Grey TAZs have no jobs. Ranges of values in the legend are quintiles. The TAZ shapefile is available from the Community of Madrid open data portal._](Presentation-images/Fig2.png){#id .class width=100%}

![_Figure 3: Spatial availability of jobs per origin and mode $V_i^m$._](Presentation-images/Fig5.png){#id .class width=98%}

@@

![_Figure 4: Proportion of population by mode and spatial availability of jobs by mode ($V_i^m$) aggregated for the city of Madrid (All), the area within the M-30 highway, and within the Centro._](Presentation-images/Fig6.png){#id .class width=100%}

@@

![_Figure 5: Distribution of spatially available jobs per capita by mode of transportatin ($v_i^m$)._](Presentation-images/Fig7.png){#id .class width=98%}

>>>>

---
title: "Multimodal spatial availability: a singly-constrained measure of accessibility considering multiple modes"
poster_height: "36in"
poster_width: "54in"
font_family: 'Rasa'
primary_colour: "#7A003C"
secondary_colour: "#d3d3d3"
accent_colour: "#FDBF57"
titlebox_bordercol: "#5E6A71"
titlebox_borderwidth: "0.2cm"
author:
  - name: Anastasia Soukhov
    affil: 1
    email: soukhoa@mcmaster.ca
    twitter: soukhov_a
    main: true
  - name: Javier Tarriño-Ortiz
    affil: 2
    email: javier.tarrino.ortiz@upm.es
  - name: Julio A. Soria-Lara
    affil: 2
    email: julio.soria-lara@upm.es
  - name: Antonio Páez
    email: paezha@mcmaster.ca
    affil: 1
affiliation:
  - num: 1
    address: Department of Earth, Environment and Society, McMaster University, Hamilton, Canada
  - num: 2
    address: Centro de Investigación del Transporte (TRANSyT), Universidad Politécnica de Madrid, Madrid, Spain
column_numbers: 4
logoright_name: images/acknowledgements-combo.png
logoleft_name: images/soukhova-LinkTree.png
sectitle_textsize: "40pt"
sectitle_borderwidth: "0.4mm"
title_textsize: "80pt"
author_textsize: "50pt"
affiliation_textsize: "40pt"
body_textsize: "35px"
link-citations: true
bibliography:
    - "`r system('kpsewhich ../bibliography/bibliography.bib', intern=TRUE)`"
output: 
  posterdown::posterdown_html:
    self_contained: true
knit: pagedown::chrome_print  #this knits the created html file into a .pdf. comment out if .pdf isn't needed
---
# Overview
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, eval=FALSE, include=FALSE}
# pagedown::chrome_print("TRB-Poster.Rmd", format = "pdf")
```
```{r load-packages, cache=FALSE, include=FALSE}
library(dplyr)
library(sf)
library(ggplot2)
library(tidyverse)
library(units)
library(patchwork)
library(ggspatial)
library(ggforce)
library(geomtextpath)
library(knitr)
library(gridExtra)
library(grid)
library(huxtable)

@@

quick_html(ht, file = "images/synth_ex_table.html", open = FALSE)
# higher zoom increases resolution and image size
webshot::webshot(url = "images/synth_ex_table.html", file = "images/synth_ex_table.png",
                 zoom = 5, selector = "table")
```
```{r, create-figure-with-toy-example, echo=FALSE, eval=FALSE, include=FALSE}
toy_example_plot <- ggplot() + 
  # Plot centers
  geom_circle(data = centers,
             aes(x0 = x, 
                 y0 = y,
                 r = radius),
             color = "grey30",
             fill = "grey90") +
  annotate(geom = "label", 
           x=c(1.5, 1.5, 10),
           y=c(9.2, 0.8, 5.2), 
           label = c("Suburban (50,000 jobs)", "Urban (100,000 jobs)", "Satellite (10,000 jobs)"),
           fill = c("turquoise1","turquoise1","turquoise1"),
           size=2.7) +
  # Connect origins and destinations with curves and put the text on curves
  geom_textcurve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group,
                   label = time),
             color = "black",
             position=position_jitter(width=0.1,height=0.1),
             size = 1.8,
             curvature = 0.20,
             linewidth = 0.5,
             linecolour = "black",
             arrow = arrow(type = "closed", angle = 10, length = unit(0.03, "npc"))) +
  # Plot origins and destinations points
  geom_point(data = od,
            aes(size = size,
                x = x, 
                y = y, 
                color = id,
                shape = type)) +
  scale_size(range = c(3, 7)) +
  scale_shape_manual(values = c("Population" = 17,'Jobs' = 16)) +
  scale_color_manual(values = c("A" = "springgreen3",
                                "B" = "springgreen4",
                                "C" = "springgreen1",
                                '1' = "turquoise1",
                                '2' = "turquoise1",
                                '3' = "turquoise1")) +
  # Label origins and destinations
  geom_text(data = od, 
            aes(x, 
                y, 
                label=id),
            size=2.5) +
  # place the table
    annotation_custom(rasterGrob(png::readPNG(source="images/synth_ex_table.png")),
                      xmin= 5.5, xmax=Inf, 
                      ymin=6, ymax=Inf
                      )+
  # Theme the plot
  coord_fixed(xlim = c(0,20), ylim=c(0,12)) + 
  theme_void() + guides(shape = "none", size = "none", color = "none", linetype ="none")

toy_example_plot
ggsave("images/toy-example.png",dpi=600)
```

@@

![_Figure 1: Calculated Hansen $S$, Shen-type $a$ and Spatial Availability $V$ assuming an impedance function of $f(c_{ij})^{\text{x}} = f(c_{ij})^{\text{z}} =exp(-0.1 \cdot c_{ij}^m)$ for the multimodal synthetic population._](images/toy-example.png){#id .class width=100%}

@@

![_Figure 2: Spatial distribution of jobs taken by people living and working in Madrid as reported in the 2018 travel survey (left) and trip length distribution (right). Grey TAZs have no jobs. Ranges of values in the legend are quintiles. The TAZ shapefile is available from the Community of Madrid open data portal._](images/Fig2.png){#id .class width=100%}

![_Figure 3: Spatial availability of jobs per origin and mode $V_i^m$._](images/Fig5.png){#id .class width=98%}

@@

![_Figure 4: Proportion of population by mode and spatial availability of jobs by mode ($V_i^m$) aggregated for the city of Madrid (All), the area within the M-30 highway, and within the Centro._](images/Fig6.png){#id .class width=100%}

@@

![_Figure 5: Distribution of spatially available jobs per capita by mode of transportatin ($v_i^m$)._](images/Fig7.png){#id .class width=98%}
